---
chapter: 1
knit: "bookdown::render_book"
---

<!--
The following line is required to re-set page numbering after preliminary material. Do not remove
-->
\clearpage\pagenumbering{arabic}\setcounter{page}{1}


# Introduction {#ch:intro}

This is where you introduce the main ideas of your thesis, and an overview of the context and background.

In a PhD, Chapter 2 would normally contain a literature review. Typically, Chapters 3--5 would contain your own contributions. Think of each of these as potential papers to be submitted to journals. Finally, Chapter 6 provides some concluding remarks, discussion, ideas for future research, and so on. Appendixes can contain additional material that don't fit into any chapters, but that you want to put on record. For example, additional tables, output, etc.

## Rmarkdown

In this template, the rest of the chapter shows how to use Rmarkdown. The big advantage of using Rmarkdown is that it allows you to include your R code directly into your thesis, to ensure there are no errors in copying and pasting, and that everything is reproducible. It also helps you stay better organized.

For details on using _R Markdown_ see <http://rmarkdown.rstudio.com>.


## Results from analyses

We can fit a dynamic regression model to the sales data.

If $y_t$ denotes the sales in quarter $t$, $x_t$ denotes the corresponding advertising budget and $z_t$ denotes the GDP, then the resulting model is:
\begin{equation}
  y_t - y_{t-4} = \beta (x_t-x_{t-4}) + \gamma (z_t-z_{t-4}) + \theta_1 \varepsilon_{t-1} + \Theta_1 \varepsilon_{t-4} + \varepsilon_t
\end{equation}
where

The `knitLatex` package is useful for generating tables from R output. Other packages can do similar things including the `kable` function in `knitr` which is somewhat simpler but you have less control over the result. If you use `knitLatex` to generate tables, don't forget to include `results="asis"` in the chunk settings.

## Unrelated Code

A plot

```{r a-plot, echo = TRUE}
library(ggplot2)
library(hrbrthemes)

ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width, fill = Species)) +
  geom_point(shape = 21, size = 2) +
  theme_ipsum(
    base_family = "Source Sans Pro"
  )
```

A table

```{r a-table, echo = knitr::is_html_output()}
library(kableExtra)

head(iris) %>%
  kable(booktabs = TRUE) %>%
  kable_styling(position = "center")
```

